---
title: "Sentiment Analysis V1"
author: "Ashley Thompson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
install.packages("readxl")
install.packages("dagitty")

library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(janitor)
library(plm)
library(dagitty)
library(fixest)



knitr::opts_chunk$set(echo = TRUE)
```

## What's the cost of bad press? 
Do social media postings impact the value of a company, and to what extent? I will explore the causal impact of adverse social media exposure on a company’s value as indicated by share prices. 

Using panel data on share price and sentiment ratings provided by Bloomberg Intelligence, I assess the influence negative sentiment has on share price. 

This will be calculated in three core steps:

1. Data cleaning and preparation: Removal of NaN values, generation of a price change figure for each time period being investigated, and the generation of a treatment dummy corresponding to negative social media sentiment (less than zero) to isolate a treatment group. 

2. Fixed effects regression: To account for differences in companies, we will run company-level fixed effects with the following time lags for treatment, 1 day, 2 days, 3 days, 5 days, 7 days

3. Exploratory analysis to further isolate the causal effect of social media sentiment: Isolated treatment effect of comments by famous people, double debiased ML application with a broad set of counfounders, and use of hourly pricing data on the most influenced stocks to isolate the immediate impact of social media sentiment from other endogenous factors affecting share price.
```{r data_prep}
#LOAD & PIVOT DATA TO LONG FORMAT

source = "/Users/ashleythompson/Desktop/Capstone/data/raw/Bloomber25MAR.xlsx"
sheet = 1               

raw = read_excel(source, sheet = sheet, col_names = FALSE)

# pull select top row fields for new columns
h1 = raw[1, ] %>% unlist(use.names = FALSE) %>% as.character()  # tickers
h3 = raw[3, ] %>% unlist(use.names = FALSE) %>% as.character()  # (PX_OPEN, PX_LAST, TWITTER_S)

# Normalize blanks
h1 = na_if(str_trim(h1), "")
h3 = na_if(str_trim(h3), "")

# Fill down ticker names
h1 = tidyr::fill(tibble(x = h1), x, .direction = "down")$x

# KEEP: date col
keep_cols = c(1, which(!is.na(h3) & seq_along(h3) != 1))

raw = raw[, keep_cols]
h1 = h1[keep_cols]
h3 = h3[keep_cols]

# reomve top three rows
dat = raw[-c(1,2,3), ]

names(dat)[1] = "date"
names(dat) = c("date", map2_chr(h1[-1], h3[-1], ~ paste0(.x, "__", .y)))

names(dat) = make.unique(names(dat), sep = "__dup__")

# convert dates to actual dates from numbers 
dat = dat %>%
    mutate(date = as.Date(as.numeric(date), origin = "1899-12-30"))

# pivot to long format
long = dat %>%
  pivot_longer(
    cols = -date,
    names_to = c("ticker", "field"),
    names_sep = "__",
    values_to = "value"
  ) %>%
  pivot_wider(names_from = field, values_from = value) %>%
  transmute(
    date = date,
    ticker = ticker,
    PX_OPEN = PX_OPEN,
    PX_CLOSE = PX_LAST,
    twitter_sent = TWITTER_SENTIMENT_DAILY_AVG
  ) %>%
  arrange(ticker, date)

long

```
# Remove NaN values
``` {r remove nans}
long = long %>%
  mutate(across(everything(), ~ na_if(as.character(.x), "#N/A N/A"))) %>%
  mutate(across(everything(), ~ na_if(.x, "#N/A"))) %>%
  mutate(across(c(PX_OPEN, PX_CLOSE, twitter_sent), ~ as.numeric(.x)))

# get rid of non trading days... which are the N/A vales
long = long %>%
  filter(!is.na(PX_OPEN), !is.na(PX_CLOSE))

```

## Compute daily return and lag returns
```{r returns}
#one day return
long = long %>%
  mutate(return = PX_CLOSE - PX_OPEN)

#lags
long = long %>%
  arrange(ticker, date) %>%
  group_by(ticker) %>%
  mutate(
    lag1 = lag(return, 1),
    lag2 = lag(return, 2),
    lag3 = lag(return, 3),
    lag5 = lag(return, 5),
    lag7 = lag(return, 7)
  ) %>%
  ungroup()
```
#Data summary
``` {r data}
summary(long)
```



# Initial Regression (PLM)

``` {r plm regression}

model_plm = plm(return ~ twitter_sent, data = long, index = c("ticker"), model = "within")
summary(model_plm)

```


``` {r fixest regression}

model_feols = feols(return ~ twitter_sent| ticker, data = long)
summary(model_feols)

```


```{r DAG}
dag {
bb="0,0,1,1"
"PX OPEN" [pos="0.380,0.477"]
"Price Trend (Last 3 days)" [pos="0.421,0.774"]
AVG_TWITTER_SENTIMENT [exposure,pos="0.532,0.668"]
CUR_MKT_CAP [pos="0.184,0.697"]
EQY_FLOAT [pos="0.183,0.526"]
PX_HIGH [pos="0.647,0.642"]
PX_LAST [pos="0.643,0.489"]
PX_LOW [pos="0.760,0.720"]
PX_VOLUME [pos="0.531,0.339"]
RETURN [outcome,pos="0.842,0.492"]
SHR_OUT [pos="0.382,0.341"]
"PX OPEN" -> AVG_TWITTER_SENTIMENT
"Price Trend (Last 3 days)" -> "PX OPEN"
"Price Trend (Last 3 days)" -> AVG_TWITTER_SENTIMENT
AVG_TWITTER_SENTIMENT -> PX_HIGH
AVG_TWITTER_SENTIMENT -> PX_LOW
AVG_TWITTER_SENTIMENT <-> PX_VOLUME
CUR_MKT_CAP -> "PX OPEN"
CUR_MKT_CAP -> AVG_TWITTER_SENTIMENT
EQY_FLOAT -> "PX OPEN"
PX_HIGH -> PX_LAST
PX_LAST -> RETURN
PX_LOW -> PX_LAST
PX_VOLUME -> PX_LAST
SHR_OUT -> PX_VOLUME
}


```